Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-21 journal/article.tex
Work in progress

@@

>>>>

S: Positive experience helps spreading transformation

* A positive experience created word-of-mouth that was spreading in the company
* Other teams took interest  --> Experience from pilot program
[P6]

* A survey was created --> The survey showed that Scrum was preferred over the old model
* This helped other teams to start with agile
[P6]

* The benefits of agile are learned
* Persons who have experenced success will work for long term establishment of agile
[P9]

* Failure of the old model was contrasted with success of Scrum
* The company decided to invest in agile
[P19]

* Positive feedback from pilot encouraged the entire organization to change
[P22]

* The teaching event was designed to be engaging
* For the interest to be maintained it was an important factor that people had fun in training
* The agile practices were chosen tactically --> Even sceptics were convinced at the end
[P32]

* The successful involvment of agile laid a foundation for further work
[P36]

* The organization saw at first hand that agile can benefit them (while the agile consulting company delivered)
* Management became interested
* There was some resistance --> Success mitigated it
* Without seeing at first hand how agile was beneficial the organization would
  never had started a transformation
[P36]

* Positive results will create interest --> The new model will spread
[P39]

* Positive word-of-mouth led to more people applying for agile project positions
[P40]

* Positivity overall is important in change
* Leaders should especially show positivity
* Celebrate even trivial successes
* Encourage toexperiment and learn from failure
[P40]

* Make benefits visible, publish success stories --> The transformation will spread
* The organization will better move towards the common goal
[P42]

* Showing good results made other teams to catch on agile
[P46]

@@

* The primary studies were quite openly pro-agile -- how large a factor of bias
  is this?
